\begin{abstract}

The significance of high quality treebanks has been steadily increasing due to their crucial role in developing natural language processing tools.
The creation of such treebanks is an enormously labor-intensive and time-consuming task due to the need for qualified annotators and the quantity of data to be annotated.
Tools that support this process have been developed, however, most of them are not suitable for annotating large treebanks of agglutinative languages such as Turkish.
Agglutinative languages require additional features for their annotation compared to the ones without agglutination.
They also require extensive annotation of their morphology and have longer dependency arc lengths, making the annotator focus essential to the process.
Low-resource agglutinative languages need suitable tools that will help their annotators to create high quality resources.
This paper describes the design and implementation of a web-based collaborative grammatical annotation tool for annotating large treebanks, which is also suitable for agglutinative languages.
This work builds on extensive experience with a previously developed grammatical annotation tool to annotate a Turkish treebank.
The main objectives of the tool are to: (1) support the creation of valid and consistent annotations, (2) increase the speed of the annotation process, (3) improve the user experience of annotators, (4) support collaboration among annotators, and (5) provide an open-source and easily deployable web-based annotation tool with a flexible application programming interface (API) to benefit the scientific community.
This paper discusses the requirements elicitation, design, implementation, and evaluation of \boatvtwo\ along with examples.
% this paper describes / discusses, good to change

\keywords{natural language processing, linguistic annotation, annotation tool, web application, dependency parsing, Universal Dependencies}

\end{abstract}
