\section{Related Work}
\label{sec:related}

Annotation tools may be characterized in terms of their accessibility and the support they provide for different languages, various annotation categories, user interface modalities, annotation related standards, multiple annotators, searching of annotations, and automation.
Adherence to standards is recommended to get the most benefit from the annotated data sources.
Universal Dependencies~\cite{UD} is an actively growing standard for annotation of treebanks that intends to cover all human languages and its support for agglutinative languages is evolving.

Many dependency annotation tools have been proposed with many of them being UD-compliant, such as brat~\cite{brat}, UD Annotatrix~\cite{ud-annotatrix} and DGA~\cite{dgannotator}.
Almost all tools are capable of annotating a variety of languages and all the tools that are detailed below do so.
They mostly require mouse-based user interactions, which is inefficient for annotation of agglutinative languages due to the need for extensive annotation for most tokens.

% 2011
ITU Treebank Annotation Tool~\cite{itu-annotation-tool} is an open-source standalone tool with 3 versions.
It was developed specifically for Turkish.
It has three stages of annotation: morphological analysis, morphological disambiguation and syntax analysis.
It offers semi-automated support for annotators through analyzers for creating new datasets as well as correcting already existing Turkish treebanks.
It mostly relies on mouse-based interactions and doesn't support the \ud\ framework.
This tool has been used to annotate the ITU Web Treebank~\cite{itu-web-tb}.
Its latest version (3) was written in Java, requiring Java to be installed on the system used for annotations.

% 2012
brat~\cite{brat} is a web-based \textit{text} annotation tool which provides a collaborative annotation environment.
Being web-based, it's usable across platforms.
It's very flexible in its annotation types and has support for many annotation tasks such as dependency, entity or coreference annotation.
It's also used for visualization of annotations.
Annotators use mouse and keyboard together to annotate.
Annotators are able to import and export their annotations in a file format called \textit{standoff} specific to brat.
It is configurable to support annotations compliant with UD and is used for visualization in the UD documentation system.
brat supports real-time collaboration, even allowing annotators to edit the same annotation.
It supports searching the documents or annotations of them with various filters.

% 2015
The Dependency Grammar Annotator~\cite{dgannotator} (also known as DGA or DgAnnotator) is a dependency annotation tool.
It enables its users to annotate POS and dependency relation tags via mouse clicks.
It supports transfer of annotations in UD compliant formats.
It doesn't support multiple annotators to work on the same treebank.
There is no search functionality.
It was written in Java~\cite{java}, and consequently requires Java.

% 2016
WebAnno~\cite{webanno} is a web-based open-source annotation tool, that is not restricted to dependency annotations but has support for morphological, syntactical, and semantic annotations also, with multi-user support.
To annotate morphological features of a token, it requires several mouse clicks which is impractical for MRLs.
The sentences to be annotated are displayed vertically in a single screen, unlike many tools that focus on a single sentence at a time.
It supports curation of annotations created by multiple annotators.
It has two installment options, standalone and server.
The standalone version requires Java, while the server version requires a Tomcat~\cite{tomcat} server with a MySQL~\cite{mysql} database.
% may want to add inception as improvement over this

% 2018
UD-Annotatrix~\cite{ud-annotatrix} is a UD-specific dependency annotation tool that aims to be simpler than brat.
Mouse usage is necessary, in addition to keyboard entries, for annotation.
It also supports real-time collaboration if the tool is deployed in a server.
It employs annotation standards of UD and CG3~\cite{cg3}
It doesn't have a search functionality.

% 2019
CoNLL-U Editor~\cite{conll-u_editor} is a web-based annotation tool, specific to the CoNLL-U~\cite{conll} format of UD.
It saves every edit of annotations by version control.
If specific lists of part-of-speech tags are provided by the annotators, it supports autocompletion during annotation.
Multiple annotators are able to annotate the same treebank, if they don't work on the same sentence at a time.
Annotators can search using any combination of linguistic tags of UD using the tool.
It requires a Java-based server.

% Olcay's paper, 2022
StarDust~\cite{stardust} is a standalone dependency annotation tool.
It uses 2 layers: morphological disambiguation and dependency annotation layers, sequentially.
In the dependency annotation layer, annotators are expected to click on a dependeny word and drag the cursor to the head word.
It stores each sentence's annotation in a different file.
For backups of the annotations, it uses Dropbox~\cite{dropbox}, which is a proprietary cloud storage platform.
There were many treebanks annotated with this tool: 1 English and 5 Turkish treebanks.

BoAT-v2 is the second iteration of \boatvone.
It improves on it by including a search functionality, a database to represent sentences in a more essential way rather than a plaintext file and an accessible web interface with an API for flexibility.
\boatvtwo\ has been developed to reduce clutter that \boatvone\ was reported to have in parts of the screen in the feedback of the previous \boatvone\ usage.

\newcolumntype{s}{>{\columncolor[HTML]{FFFAF0}} p{2.8cm}}
% FFFAF0 : floral white
\begin{table}[h]
    \label{table:rel-work}
    \centering
    \begin{tabular}{|s|>{\centering\arraybackslash} p{1.1cm}|>{\centering\arraybackslash} p{1.6cm}|>{\centering\arraybackslash} p{2.4cm}|>{\centering\arraybackslash} p{1.9cm}|>{\centering\arraybackslash} p{1.2cm}|}
       \hline
        \rowcolor[HTML]{FFFAF0} \multicolumn{6}{|c|}{\textbf{Comparison of Annotation Tools}} \\ \hline\hline
        \multicolumn{1}{|c|}{\cellcolor[HTML]{FFFAF0} \textbf{Tool}} & \textbf{Mouse} & \textbf{Keyboard} & \textbf{Standards} & \textbf{Multi-user} & \textbf{Search} \\\hline
        brat & + & + & Extendable & + & + \\\hline
        UD Annotatrix & + & + & UD \& CG3 & + & - \\\hline
        DgAnnotator & + & - & UD & - & - \\\hline
        CoNLL-U Editor & + & + & UD & + & + \\\hline
        ITU & + & + & UD & - & - \\\hline
        WebAnno & + & + & UD & + & - \\\hline
        StarDust & + & + & - & - & - \\\hline
        \boatvtwo\ & + & + & UD & + & + \\\hline
    \end{tabular}
    \caption{Properties of above-mentioned annotation tools}
\end{table}
