
\begin{thebibliography}{99}

\bibitem{anon} Anonymous. We're not including this reference to preserve anonymity for the review process.

\bibitem{altnlp} Akkurt SF, Marşan B, Uskudarli S. Boat v2 - A web-based dependency annotation tool with focus on agglutinative languages. In: Agglutinative Language Technologies as a challenge of Natural Language Processing (ALTNLP); Slovenia; 2022. https://doi.org/10.48550/arXiv.2207.01327

\bibitem{brat} Stenetorp P, Pyysalo S, Topi\'{c} G, Ohta T, Ananiadou S et al. brat: a web-based tool for nlp-assisted text annotation. In: Proceedings of the Demonstrations Session at EACL; Avignon, France; 2012. Association for Computational Linguistics.

\bibitem{conll-u_editor} Heinecke J. Conllueditor: a fully graphical editor for universal dependencies treebank files. In: Universal Dependencies Workshop; Paris; 2019.

\bibitem{itu-annotation-tool} Pamay T, Sulubacak U, Toruno{\u{g}}lu-Selamet D, Eryi{\u{g}}it G. The annotation process of the itu web treebank. In: Proceedings of The 9th Linguistic Annotation Workshop; Denver, Colorado, USA; 2015. Association for Computational Linguistics, pp. 95-101. https://doi.org/10.3115/v1/W15-1610

\bibitem{conll} Buchholz S, Marsi E. Conll-x shared task on multilingual dependency parsing. In: Proceedings of the Tenth Conference on Computational Natural Language Learning (CoNLL-X); New York City; 2006. Association for Computational Linguistics, pp. 149-164.

\bibitem{stardust} Yenice AB, Cesur N, Kuzgun A, Y{\i}ld{\i}z OT. Introducing stardust: a ud-based dependency annotation tool. In: Proceedings of the 16th Linguistic Annotation Workshop (LAW-XVI) within LREC2022; Marseille, France; 2022. European Language Resources Association; pp. 79-84.

\bibitem{ud-annotatrix} Francis MT, Mariya S, Jonathan NW. Ud annotatrix: an annotation tool for universal dependencies. In: Proceedings of the 16th International Workshop on Treebanks and Linguistic Theories (TLT16); 2018; pp. 10-17.

\bibitem{bootstrap} Bootstrap (2022). Bootstrap [online]. Website https://getbootstrap.com/docs/5.1 [accessed 05 May 2022].

\bibitem{cg3} Didriksen T (2022). Constraint Grammar Manual [online]. Website https://visl.sdu.dk/cg3/single/ [accessed 18 November 2022].

\bibitem{dgannotator} Attardi G (2022). {DgAnnotator} [online]. Website http://medialab.di.unipi.it/Project/QA/Parser/DgAnnotator/ [accessed 27 March 2022].

\bibitem{django} Django Software Foundation (2022). Django documentation [online]. Website https://docs.djangoproject.com/en/4.0 [accessed 25 March 2022].

\bibitem{django-filter} Alex Gaynor, Carlton Gibson and others (2022). django-filter [online]. Website https://docs.djangoproject.com/en/4.0 [accessed 24 April 2022].

\bibitem{docker} Docker Inc. (2022). Docker [online]. Website https://www.docker.com [accessed 2 May 2022].

\bibitem{drf} Encode OSS Ltd. (2022). Django REST framework [online]. Website https://www.django-rest-framework.org [accessed 27 March 2022].

\bibitem{dropbox} Dropbox, Inc. (2022). Dropbox.com [online]. Website http://dropbox.com [accessed 18 November 2022].

\bibitem{psql} The PostgreSQL Global Development Group (2022). PostgreSQL [online]. Website https://www.postgresql.org/docs [accessed 27 March 2022].

\bibitem{mysql} Oracle (2022). MySQL [online]. Website https://www.mysql.com/ [accessed 16 December 2022].

\bibitem{tomcat} The Apache Software Foundation (2022). Apache Tomcat® [online]. Website https://tomcat.apache.org/ [accessed 16 December 2022].

\bibitem{java} Oracle (2022). Oracle Java Technologies [online]. Website https://www.oracle.com/java/technologies/ [accessed 16 December 2022].

\bibitem{python} Python Software Foundation (2022). Python [online]. Website https://www.python.org [accessed 24 April 2022].

\bibitem{qt} The Qt Company (2022). Qt [online]. Website https://www.qt.io/ [accessed 25 May 2022].

\bibitem{spacy} Explosion (2022). spaCy [online]. Website https://spacy.io [accessed 27 March 2022].

\bibitem{spyssalo} Pyysalo S (2022). conllu.js [online]. Website http://spyysalo.github.io/conllu.js [accessed 25 March 2022].

\bibitem{ud} Universal Dependencies (2022). UD [online]. Website https://universaldependencies.org [accessed 2 May 2022].

\bibitem{ud-tools} Universal Dependencies (2022). UD tools [online]. Website https://universaldependencies.org/tools [accessed 22 April 2022].

\bibitem{webanno} WebAnno (2022). WebAnno [online]. Website https://webanno.github.io/webanno/documentation [accessed 5 May 2022].

\bibitem{atis-en} Universal Dependencies (2021). UD English Atis [online]. Website https://universaldependencies.org/treebanks/en\_atis/index.html [accessed 4 Jan 2023].

\bibitem{atis-tr} Universal Dependencies (2021). UD Turkish Atis [online]. Website https://universaldependencies.org/treebanks/tr\_atis/index.html [accessed 4 Jan 2023].

\bibitem{pud-en} Universal Dependencies (2021). UD English PUD [online]. Website https://universaldependencies.org/treebanks/en\_pud/index.html [accessed 4 Jan 2023].

\bibitem{pud-tr} Universal Dependencies (2021). UD Turkish PUD [online]. Website https://universaldependencies.org/treebanks/tr\_pud/index.html [accessed 4 Jan 2023].

\bibitem{macos} Apple Inc. (2022). macOS [online]. Website https://www.apple.com/macos/ [accessed 5 Jan 2023].

\bibitem{safari} Apple Inc. (2022). Safari [online]. Website https://www.apple.com/safari/ [accessed 5 Jan 2023].

\bibitem{windows} Microsoft (2022). Windows [online]. Website https://www.microsoft.com/en-us/windows [accessed 5 Jan 2023].

\bibitem{chrome} Google (2022). Google Chrome [online]. Website https://www.google.com/chrome/ [accessed 5 Jan 2023].

\bibitem{selenium} Selenium (2022). Software Freedom Conservancy [online]. Website https://www.selenium.dev/ [accessed 5 Jan 2023].

\end{thebibliography}
