\begin{thebibliography}{99}
\bibitem{anon} Anonymous. We're not including this reference to preserve anonymity for the review process.
\bibitem{altnlp} Akkurt SF, Marşan B, Uskudarli S. Boat v2 - A web-based dependency annotation tool with focus on agglutinative languages. In: Agglutinative Language Technologies as a challenge of Natural Language Processing (ALTNLP); Slovenia; 2022. doi.org/10.48550/arXiv.2207.01327
\bibitem{brat} Stenetorp P, Pyysalo S, Topi\'{c} G, Ohta T, Ananiadou S et al. brat: a web-based tool for nlp-assisted text annotation. In: Proceedings of the Demonstrations Session at EACL; Avignon, France; 2012. Association for Computational Linguistics.
\bibitem{conll-u_editor} Heinecke J. Conllueditor: a fully graphical editor for universal dependencies treebank files. In: Universal Dependencies Workshop; Paris; 2019.
\bibitem{itu-annotation-tool} Pamay T, Sulubacak U, Toruno{\u{g}}lu-Selamet D, Eryi{\u{g}}it G. The annotation process of the itu web treebank. In: Proceedings of The 9th Linguistic Annotation Workshop; Denver, Colorado, USA; 2015. Association for Computational Linguistics, pp. 95-101. doi.org/10.3115/v1/W15-1610
\bibitem{conll} Buchholz S, Marsi E. Conll-x shared task on multilingual dependency parsing. In: Proceedings of the Tenth Conference on Computational Natural Language Learning (CoNLL-X); New York City; 2006. Association for Computational Linguistics, pp. 149-164.
\bibitem{stardust} Yenice AB, Cesur N, Kuzgun A, Y{\i}ld{\i}z OT. Introducing stardust: a ud-based dependency annotation tool. In: Proceedings of the 16th Linguistic Annotation Workshop (LAW-XVI) within LREC2022; Marseille, France; 2022. European Language Resources Association; pp. 79-84.
\bibitem{turk-2021-boat} T{\"u}rk U, Atmaca F, {\"O}zate{\c{s}} {\c{S}}B, Berk G, Bedir ST et al. Resources for turkish dependency parsing: introducing the boun treebank and the boat annotation tool. In: Language Resources and Evaluation; Springer; pp 1-49.
\bibitem{ud-annotatrix} Francis MT, Mariya S, Jonathan NW. Ud annotatrix: an annotation tool for universal dependencies. In: Proceedings of the 16th International Workshop on Treebanks and Linguistic Theories (TLT16); 2018; pp. 10-17.
\bibitem{bootstrap} Bootstrap (2022). Bootstrap [online]. Website getbootstrap.com/docs/5.1 [accessed 05 May 2022].
\bibitem{cg3} Didriksen T (2022). Constraint Grammar Manual [online]. Website visl.sdu.dk/cg3/single [accessed 18 November 2022].
\bibitem{dgannotator} Attardi G (2022). {DgAnnotator} [online]. Website medialab.di.unipi.it/Project/QA/Parser/DgAnnotator [accessed 27 March 2022].
\bibitem{django} Django Software Foundation (2022). Django documentation [online]. Website docs.djangoproject.com [accessed 25 March 2022].
\bibitem{django-filter} Alex Gaynor, Carlton Gibson and others (2022). django-filter [online]. Website django-filter.readthedocs.io [accessed 24 April 2022].
\bibitem{docker} Docker Inc. (2022). Docker [online]. Website docker.com [accessed 2 May 2022].
\bibitem{drf} Encode OSS Ltd. (2022). Django REST framework [online]. Website django-rest-framework.org [accessed 27 March 2022].
\bibitem{dropbox} Dropbox, Inc. (2022). Dropbox.com [online]. Website dropbox.com [accessed 18 November 2022].
\bibitem{psql} The PostgreSQL Global Development Group (2022). PostgreSQL [online]. Website postgresql.org/docs [accessed 27 March 2022].
\bibitem{mysql} Oracle (2022). MySQL [online]. Website mysql.com [accessed 16 December 2022].
\bibitem{tomcat} The Apache Software Foundation (2022). Apache Tomcat® [online]. Website tomcat.apache.org [accessed 16 December 2022].
\bibitem{java} Oracle (2022). Oracle Java Technologies [online]. Website oracle.com/java/technologies [accessed 16 December 2022].
\bibitem{python} Python Software Foundation (2022). Python [online]. Website python.org [accessed 24 April 2022].
\bibitem{qt} The Qt Company (2022). Qt [online]. Website qt.io [accessed 25 May 2022].
\bibitem{spacy} Explosion (2022). spaCy [online]. Website spacy.io [accessed 27 March 2022].
\bibitem{spyssalo} Pyysalo S (2022). conllu.js [online]. Website spyysalo.github.io/conllu.js [accessed 25 March 2022].
\bibitem{tulap} Boğaziçi University (2022). TABILAB Repository Home [online]. Website tulap.cmpe.boun.edu.tr [accessed 24 April 2022].
\bibitem{ud} Universal Dependencies (2022). UD [online]. Website universaldependencies.org [accessed 2 May 2022].
\bibitem{ud-tools} Universal Dependencies (2022). UD tools [online]. Website universaldependencies.org/tools [accessed 22 April 2022].
\bibitem{webanno} WebAnno (2022). WebAnno [online]. Website webanno.github.io/webanno/documentation [accessed 5 May 2022].
\bibitem{ud-turkish-boun} Universal Dependencies (2022). UniversalDependencies/UD\_Turkish-BOUN GitHub Repository [online]. Website github.com/UniversalDependencies/UD\_Turkish-BOUN [accessed 25 May 2022].
\bibitem{atis-en} Universal Dependencies (2021). UD English Atis [online]. Website github.com/UniversalDependencies/UD\_English-ATIS [accessed 4 Jan 2023].
\bibitem{atis-tr} Universal Dependencies (2021). UD Turkish Atis [online]. Website github.com/UniversalDependencies/UD\_Turkish-ATIS [accessed 4 Jan 2023].
\bibitem{pud-en} Universal Dependencies (2021). UD English PUD [online]. Website github.com/UniversalDependencies/UD\_English-PUD [accessed 4 Jan 2023].
\bibitem{pud-tr} Universal Dependencies (2021). UD Turkish PUD [online]. Website github.com/UniversalDependencies/UD\_Turkish-PUD [accessed 4 Jan 2023].
\bibitem{macos} Apple Inc. (2022). macOS [online]. Website apple.com/macos [accessed 5 Jan 2023].
\bibitem{safari} Apple Inc. (2022). Safari [online]. Website apple.com/safari [accessed 5 Jan 2023].
\bibitem{windows} Microsoft (2022). Windows [online]. Website microsoft.com/en-us/windows [accessed 5 Jan 2023].
\bibitem{chrome} Google (2022). Google Chrome [online]. Website google.com/chrome [accessed 5 Jan 2023].
\bibitem{selenium} Selenium (2022). Software Freedom Conservancy [online]. Website selenium.dev [accessed 5 Jan 2023].
\end{thebibliography}