\documentclass[a4paper,onesided,12pt]{report}
\usepackage{styles/fbe_tez}
\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
\renewcommand{\labelenumi}{(\roman{enumi})}
\usepackage{amsmath, amsthm, amssymb}
 % Some extra symbols
\usepackage[bottom]{footmisc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{longtable}
\graphicspath{{figures/}} % Graphics will be here

\usepackage{multirow}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algorithmic}
%\pagestyle{empty}
%\includeonly{introduction} % To only process the given file

\newtheorem{thm}{Theorem}[chapter]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
% COVER PAGE
\title{A Web Application for Annotating Dependency Parse Treebanks}
\turkcebaslik{..} % TODO
\author{Salih Furkan Akkurt}
\program{Computer Engineering}
\subyear{Spring 2022}

% APPROVED BY PAGE
\supervisor{Prof. Suzan Uskudarli}
\dateofapproval{14.02.2022}

\begin{document}

\pagenumbering{roman}
\makebstitle  % B.S. project
\makeapprovalpage
\begin{acknowledgements}
Acknowledgements.
\end{acknowledgements}

\input{sections/abstract}

\begin{ozet}
    Turkish abstract.
\end{ozet}
\tableofcontents
\listoffigures
\listoftables
\begin{symbols}

\sym{$a$}{Just a symbol}

\end{symbols}

\begin{abbreviations}
\sym{CoNLL}{Computational Natural Language Learning}
\end{abbreviations}

\chapter{INTRODUCTION AND MOTIVATION}
\label{chapter:introduction}
\pagenumbering{arabic}
\begin{itemize}
\item General overview about the topic. Describe the problem.
\item Economic aspects and environmental, social and health aspects
\end{itemize}

\chapter{STATE OF THE ART}
\label{chapter:state-of-the-art}
\begin{itemize}
\item General overview about research papers and tools
\item Technical aspects and multi-disciplinary aspects
\item Shortcomings of the state-of-the-art
\end{itemize}

\chapter{METHODS}
\label{chapter:methods}
\begin{itemize}
\item Methods needed to develop for acquiring the desired results.
\item How experiments designed.
\item Ethical guidelines followed if experiments conducted with humans.
\item Methods used to analyze and interpret the collected experimental data.
\end{itemize}

\chapter{RESULTS}
\label{chapter:method}
\begin{itemize}
\item Results achieved.
\item Compare results with the state-of-the-art.
\end{itemize}

\chapter{CONCLUSION AND DISCUSSION}
\label{chapter:method}
\begin{itemize}
\item Interpret results.
\item Potential impact in a societal context considering economic, political, environmental, and sustainability.
\end{itemize}

\chapter{FUTURE WORK}
\label{chapter:method}
\begin{itemize}
\item Outlook
\item Draw conclusions beyond project horizon
\end{itemize}

\bibliographystyle{styles/fbe_tez_v11}
\bibliography{references}

\appendix
\chapter{DATA AVAILABILITY STATEMENT}
\begin{itemize}
\item How data can be accessed by others.
\end{itemize}


%\appendix
\chapter{STANDARDS, LAWS, REGULATIONS AND DIRECTIVES}
\begin{itemize}
\item Any standards, laws, regulations and/or directives used.
\end{itemize}

\end{document}
