\documentclass[final,2p]{article}
%\documentclass[global,twocolumn,referee]{svjour}
% Remove option referee for final version
%
% Remove any % below to load the required packages
\usepackage{latexsym}
\usepackage{graphics}
\usepackage{graphicx,times,amsmath}
\usepackage{algorithm}
\usepackage{float}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{color}

\usepackage{amssymb,amsmath}
\usepackage{bbm}
\usepackage{multirow}
\usepackage{float}
\usepackage{bbm}
\usepackage[T1]{fontenc}  % access \textquotedbl
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{hhline}
\usepackage{url}
\usepackage{rotating}
\usepackage{hhline,multirow}
\usepackage{algpseudocode}
\usepackage[english]{babel}
\usepackage{hyphenat}
\usepackage{qtree}
\usepackage {tikz}
\usepackage{listings}
\usepackage{graphicx}

\usepackage[utf8]{inputenc}



\newlength{\marg}
\setlength{\marg}{60mm}
\newlength{\margv}
\setlength{\margv}{50mm}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-\marg}

\setlength{\oddsidemargin}{0.50\marg}
\setlength{\evensidemargin}{0.50\marg}

\addtolength{\oddsidemargin}{-1in}
\addtolength{\evensidemargin}{-1in}

\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-\margv}

\setlength{\topmargin}{0.50\margv}
\addtolength{\topmargin}{-1in}
\addtolength{\topmargin}{-\headsep}
\addtolength{\topmargin}{-\headheight}


\newcommand{\todo}[1]{\noindent\colorbox{cyan}{\parbox{\columnwidth}{#1}}}


\newcommand{\smallcapsfont}[1]{\begin{small}\textsc{\texttt{#1}}\end{small}}
\newcommand{\comment}{\emph}
\newcommand{\response}{\noindent \textbf}

\setlength{\parindent}{0pt} \setlength{\parskip}{5pt}

%\input{commands}

\begin{document}
%
\title{BoAT v2 - A Web-Based Dependency Annotation Tool with Focus on Agglutinative Languages}%\medskip
\author{Salih Furkan Akkurt, Büşra Marşan and Susan Uskudarli}
\date{27 May 2022}

\maketitle

\textbf{Point-to-Point responses to the reviewers' comments}\\\\

% \section{Authors' Comments for the Reviewers}

Dear Editor and Referees,

We thank you for your encouraging comments. 
We have tried our best to address all the issues and suggestions raised by our reviewers. 
Additionally, during our revision, we made a few corrections and improvements to improve the clarity and flow of the paper. 
The following details our Point-to-Point responses to the issues identified by our reviewers, followed by general improvements.

Authors

\section*{\fbox{Review 1}}

\comment{With the Turkish language as test case, the authors present the design and development of an open-source web-based annotation tool that is based on an earlier toolkit (BoAT v1).}

\comment{The toolkit is beneficial to researchers. However, as mentioned in the paper, it is still in the testing phase.}

\comment{It would be helpful if the authors can also present initial results of any user acceptance test conducted. This is important since once of the objectives mentioned in the abstract is "significantly improve the user experience of the annotator".}

\response{We have conducted initial user acceptance tests in the meantime and included the results.}

\comment{Another suggestion: Since the toolkit was based on the experiences from BoAT v1, allotting a separate section to discuss BoAT v1 is recommended. Briefly discussing it in the Related Work section is insufficient.}

\response{We have allocated a new section for BoAT v1 with extra content where we explain the tool in more detail and included a screenshot from it in the appendix.}

\section*{\fbox{Review 2}}

\comment{The paper presents the second version of the BoAT tool. It is a collaborative dependency annotation tool designed and implemented to work with agglutinative languages. For that, the authors have taken into account experts' feedback and experience. It is an interesting paper that presents the progress done in relation to the previous version of the tool.}

\comment{As it is the second version of the tool, it is not clear if all the functionalities described in the paper are new or some of them already were part of the first version. This aspect should be clarified a little bit more.}

\response{We have elaborated on which features are new and which ones had already existed.}

\comment{Some parts of the paper needs a little bit of rephrasing. I have noticed for instance minor edition needs such as:}

\comment{In the introduction concepts/terms such as "UPOS" or "FEATS" are mentioned before properly introducing the universal dependencies framework or tags.}

\response{We have added explanations for these tags. TODO: Probably need to introduce UD.}

\comment{The API acronym is "explained" in the sentence: It has an application programming interface (API) for programmatic access and extensibility. But the acronyms is introduced in the previous paragraph.}

\response{We have moved the brief explanation of API to the first time we mention it in the paper.}

\comment{What does "MRL" refer to?}

\response{MRL is an acronym for morphologically rich languages. We have added the full version the first time we mention it in the paper.}

\comment{etc.}

\comment{All in all an interesting paper that needs a little bit of rewriting.}

\end{document}
